---
title: "Prediction-Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Prediction-Assignment-Writeup
The goal of this project is to predict the manner in which people did the exercise. This is the "classe" variable in the training set. I used 58 variables as predictors to predict the "classe" output. I used the prediction model to predict 20 different test cases of Quiz 4, and I got 100% correct prediction.

### Load packages
```{r}
library(lattice)
library(ggplot2)
library(caret)
library(e1071)
```

### Random seeding 
```{r }
set.seed(12335)
```

### Read train and test data
```{r }
training = read.csv('pml-training.csv')
testing = read.csv('pml-testing.csv')
```

### Perform data cleaning
```{r }
trn <- training[ , colSums(is.na(training)) == 0]
trn2 = subset(trn, select = -c(max_yaw_forearm, min_yaw_forearm, amplitude_yaw_forearm, kurtosis_roll_forearm, kurtosis_picth_forearm, kurtosis_yaw_forearm, skewness_roll_forearm, skewness_pitch_forearm, skewness_yaw_forearm, kurtosis_roll_dumbbell, kurtosis_picth_dumbbell, kurtosis_yaw_dumbbell, skewness_roll_dumbbell, skewness_pitch_dumbbell, skewness_yaw_dumbbell, max_yaw_dumbbell, min_yaw_dumbbell, amplitude_yaw_dumbbell, kurtosis_roll_arm, kurtosis_picth_arm, kurtosis_yaw_arm, skewness_roll_arm, skewness_pitch_arm, skewness_yaw_arm, kurtosis_roll_belt, kurtosis_picth_belt, kurtosis_yaw_belt, skewness_roll_belt, skewness_roll_belt.1, skewness_yaw_belt, max_yaw_belt, min_yaw_belt, amplitude_yaw_belt, X, cvtd_timestamp))
tst <- testing[ , colSums(is.na(testing)) == 0]
tst2 <- subset(tst, select = -c(cvtd_timestamp,X))
```
### Perform Data Partitioning
```{r}
newTraining <- createDataPartition(trn2$classe, p = 0.8, list = FALSE)
train <- trn2[newTraining,]
test <- trn2[-newTraining,]
```

### Train the data
I have used three different methods to analyze the data, which inclue LDA, GBM and RF. For this work I used 7 fold cross-validation. The following code lines for all three methods are exactly the same, and only the name of the method in modelFit line has changed. Therefore, here I only present the lines for the LDA method. 

```{r }
train_control <- trainControl(method="cv", number = 7)
modelFitLDA <- train(classe ~ ., data = train, method = "lda", trControl = train_control)
modelFitLDA$finalModel
```

### Test the fitting results
```{r }
predLDATest <- predict(modelFitLDA, newdata = test)
confusionMatrixTest <- confusionMatrix(test$classe, predLDATest)
confusionMatrixTest$table

predLDATrain <- predict(modelFitLDA, newdata = train)
confusionMatrixTest <- confusionMatrix(train$classe, predLDATrain)
confusionMatrixTest$table
```

Useing the above coding with method GBM, I could answer the Quiz 4 questions with 100%. accuracy.